\documentclass[11pt]{article}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	urlcolor=cyan
	}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}

\setlength{\parindent}{0pc}
\setlength{\parskip}{10pt}

\title{STAT157 HW 10}
\date{March 28, 2022}

\begin{document}

\maketitle

\hfill \textbf{Predictions due Monday, April 4 11:59pm}

\hfill \textbf{Gradescope submission due 15 min after}


This week's homework assignment is shorter than usual, with only the following Predictions section. Please use the time that you would have spent on a normal length homework to work on your final projects.


\section*{Predictions}

\emph{Expected completion time: 90 minutes}

Register the following predictions. You can submit them by going to \href{https://docs.google.com/forms/d/e/1FAIpQLSeAvSCrPasO4gNeqa_SrJIrslxGWjF-MRO8UQvhh9Gx3-JA_A/viewform?usp=sf_link}{this URL} and following the form's instructions. For these predictions, (and all predictions about the future throughout this class), we encourage you to use external sources -- by googling things, reading news articles, talking to friends who follow politics or music stats, etc.

\begin{enumerate}
	\item Will the new \href{https://www.cityofberkeley.info/Home.aspx}{City of Berkeley website} go live by April 20?
	\begin{itemize}
		\item This question will resolve negatively if the home page still contains the same red sidebar with ``311 City Services'' on top of ``Quick Links''.
	\end{itemize} 
	\item Will the Red Hot Chilli Peppers be expected on the lineup of the 2022 Austin City Limits festival by April 20?
	\begin{itemize}
		\item This question resolves positively if (1) the lineup is announced by EOD April 20 and Red Hot Chilli Peppers are on it, \emph{or} (2) the Red Hot Chilli Peppers are moved to the Expected section of \href{https://www.reddit.com/r/aclfestival/comments/s6izhl/official_acl_2022_lineup_speculation_thread/}{this post} by EOD April 20.
	\end{itemize}
	\item Will TSA completely or partially \href{https://www.tsa.gov/news/press/statements/2022/03/10/statement-regarding-face-mask-use-public-transportation}{re-extend the mask mandate directive} for public transportation beyond April 18?
	\begin{itemize}
		\item The question will resolve positively if there is a re-extension in some cases but not others. It will resolve negatively if there is no announcement, or an announcement stating that there will no longer be a mask mandate for public transportation.
	\end{itemize}
\end{enumerate}

For each question, submit your probability, as well as an explanation of your reasoning (1-2 paragraphs). \textbf{Please include a copy of your google form responses with your Gradescope submission.} On Gradescope, please also submit the time it took to complete this exercise.



\end{document}
