\documentclass[11pt]{article}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\setlength{\parindent}{0pc}
\setlength{\parskip}{6pt}

\begin{document}

\section*{STAT157 Syllabus: Spring 2022}

Forecasting has been used to predict elections, climate change, and the spread of COVID-19. Poor forecasts led to the 2008 financial crisis. In our daily lives, good forecasting ability can help us plan our work, be on time to events, and make informed career decisions. This practically-oriented class will provide you with tools to make good forecasts.

{\bf Instructors:} Jacob Steinhardt, Yan Zhang, and Danny Hernandez\\ {\bf GSIs:} Frances Ding, Jean-Stanislas Denain, and Collin Burns\\
\\
{\bf Drop policy (IMPORTANT):} Since there is a waitlist for the class, all students who do not turn in Homework 1 will be automatically dropped from the roster.

\subsubsection*{Lecture}

MWF11-12, in 3108 Etcheverry Hall

Zoom link for first 2 weeks of class is \href{https://berkeley.zoom.us/j/93592932586?pwd=Y1hBNEp4OGVqWHMvOXZKcmd1L0d6QT09}{here}.

This class will be heavily disussion-based. Monday and Wednesday lectures will be a combination of traditional lecture and group activities, 
while Friday will be student-led small group discussions with instructors helping to facilitate. {\bf Participation in Friday discussions} 
will count towards the grade (we'll provide make-up activities for students who need to skip due to COVID-19 exposure).

There will be no official lab / discussion block, but some homework will involve programming and we will have GSIs available during the lab slot to help students debug.

\subsubsection*{Homework}

There will be weekly homework assignments as well as weekly forecasting exercises.

\subsubsection*{Grades}

Instead of exams, there will be a final project. Students in Stat260 will be expected to do a more substantial project. %
%
Grades will be based on a combination of:
\begin{itemize} 
\item Discussion participation (15\%)
\item Forecasting Performance (20\%)
\item Homework (35\%)
\item Final project (30\%)
\end{itemize}

There will also be extra credit opportunities later in the semester.

\subsubsection*{Staff Contact}

To reach course staff, you can email \url{forecasting-class-staff@lists.berkeley.edu}. If possible, please avoid emailing professors or GSIs directly!

\end{document}
