\documentclass[11pt]{article}
	\usepackage{amsmath,amsfonts,amssymb,amsthm,bm}
	\usepackage{hyperref}
	\usepackage[margin=1in]{geometry}
	\usepackage{graphicx}
	\usepackage{amsmath,amssymb,}
	\usepackage{latexsym,color,minipage-marginpar,caption,multirow,verbatim}
	\usepackage{enumerate}

	\newcommand{\cP}{\mathcal{P}}
	\newcommand{\cX}{\mathcal{X}}
	\newcommand{\R}{\mathbb{R}}
	\newcommand{\E}{\mathbb{E}}
	\newcommand{\N}{\mathbb{N}}
	\newcommand{\rmd}{\mathrm{d}}
	\newcommand{\Cov}{\text{Cov}}
	\newcommand{\simiid}{\overset{\text{i.i.d.}}{\sim}}


	\usepackage[dvipsnames]{xcolor}
	\newcommand{\red}{\color{red}}
	\newcommand{\black}{\color{black}}
	\newcommand{\blue}{\color{MidnightBlue}}
	\newcommand{\jean}[1]{{\color{blue} [Jean: #1]}}

	\setlength{\parindent}{0pc}
	\setlength{\parskip}{10pt}

\title{STAT157/260 Project Proposal}
\date{\today}

\begin{document}

\maketitle

\begin{flushright}
	\textbf{due Wednesday, April 12th at 11:59pm}
\end{flushright}

For your project proposal, please include the following information in a document about a half-page
long, and no longer than 1 page:
\begin{itemize}
	\item The names of your group members.
	\item The option you are choosing.
	\item For the first option, \textbf{in-depth long term forecast}: A brief description of the forecasting question you are addressing. You do not need to have precise resolution criteria yet, but you should convey some background information about the forecast, and why you are interested in it. Additionally describe the steps you will take to investigate the question.
	\item For the second option, \textbf{research-style project}: A brief description of your proposal, which should include a clear statement of the question you will investigate, and an outline of the steps you plan to take.
\end{itemize}

Only one member of each group needs to submit the proposal to Gradescope. Please create a group
submission on the “Project Proposal” Gradescope assignment including all your group members.

\end{document}
